Networked Character Devices

### 2011-12-10 report/presentation.tex
added more to intro slides

\begin{frame}{\bf NCD Goals}
  \begin{itemize}
    \item<1-> Export any character device (or file) from a server over IP
    \begin{itemize}
      \item<2-> Client has exclusive access
      \item<3-> User-level advertisment, kernel-level functionality
    \end{itemize}
    \item<4-> Non-locality should be transparent to client's user level operations    
    \begin{itemize}
      \item<5-> Imported devices are accessed as local devices
      \item<6-> All client device accesses are intercepted by kernel module and sent over network
      \item<7-> Server has no access so write conflicts are not a problem
    \end{itemize}
  \end{itemize}
\end{frame}

\begin{frame}{\bf NCD Overview}
  \begin{itemize}
    \item<1-> Motivation: providing transparent access to remote devices opens up a new paradigm of storage and device usage
    \begin{itemize}
      \item<2-> Physical locality only needed for lower latency
    \end{itemize}
    \item<3-> Project attributes:
    \begin{itemize}
      \item<4-> Client: kernel module (Linux 2.6.x+)
      \item<5-> Server: userspace daemon
      \item<6-> Current Project Status:
        \begin{itemize}
          \item<7-> Successful implementation
          \item<8-> Rough around the edges
          \item<9-> More development required for certain devices
          \item<10-> Very clear focus for future work
        \end{itemize}
      \end{itemize}
  \end{itemize}
\end{frame}

\begin{frame}{Related Work}
  \begin{itemize}
    \item NFS
    \begin{itemize}
      \item Access to remote file system, but no devices
      \item Safe access
      \item http://nfs.sourceforge.net/
    \end{itemize}
    \item NBD
    \begin{itemize}
      \item Network Block Device- Introduced in Linux kernel 2.1.101
      \item Works with any file system but no exclusive access 
      \item http://nbd.sourceforge.net/
    \end{itemize}
    \item CUSE
    \begin{itemize}
      \item Character Device in User Space (extension of FUSE)- Linux kernel 2.6.31
      \item http://lwn.net/Articles/308445/
    \end{itemize}
    \item USB/IP Project
    \begin{itemize}
      \item USB device sharing over IP
      \item http://usbip.sourceforge.net/
    \end{itemize}

>>>>

\begin{frame}{\bf NCD Goals}
  \begin{itemize}
    \item<1-> Export any character device (or file) from a server over IP
    \begin{itemize}
      \item<2-> Mouse, Webcam, keyboard, USB flash drive, Xbox Kinect, monitor, external HD, etc...
      \item<3-> Client has exclusive access
      \item<4-> User-level advertisment, kernel-level functionality
    \end{itemize}
    \item<5-> Non-locality should be transparent to client's user level operations    
    \begin{itemize}
      \item<6-> Imported devices are accessed as local devices
      \item<7-> All client device accesses are intercepted by kernel module and sent over network
      \item<8-> Server user-space daemon accesses device to emulate client
      \item<9-> Server should have no other access so write conflicts are not a problem
    \end{itemize}
  \end{itemize}
\end{frame}

\begin{frame}{\bf NCD Overview}
  \begin{itemize}
    \item<1-> Motivation: providing transparent access to remote devices opens up a new paradigm of storage and device usage
    \begin{itemize}
      \item<2-> Physical locality only needed for lower latency
    \end{itemize}
    \item<3-> Project attributes:
    \begin{itemize}
      \item<4-> Client: kernel module (Linux 2.6.x+)
      \item<5-> Server: userspace daemon
      \item<6-> Current Project Status:
        \begin{itemize}
          \item<7-> Successful implementation
          \item<8-> Rough around the edges
          \item<9-> More development required for certain devices
          \item<10-> Groundwork laid for exporting all devices
          \item<11-> Very clear focus for future work
        \end{itemize}
      \end{itemize}
  \end{itemize}
\end{frame}

\begin{frame}{Related Work}
  \begin{itemize}
    \item NFS
    \begin{itemize}
      \item Access to remote file system, but no devices
      \item Safe access
      \item http://nfs.sourceforge.net/
    \end{itemize}
    \item NBD
    \begin{itemize}
      \item Network Block Device- Introduced in Linux kernel 2.1.101
      \item Works with any file system but no exclusive access 
      \item http://nbd.sourceforge.net/
    \end{itemize}
    \item CUSE
    \begin{itemize}
      \item Character Device in User Space (extension of FUSE)- Linux kernel 2.6.31
      \item Used for OSS proxy for remote sound systems
      \item http://lwn.net/Articles/308445/
    \end{itemize}
    \item USB/IP Project
    \begin{itemize}
      \item USB device sharing over IP
      \item http://usbip.sourceforge.net/
    \end{itemize}
